\ourlongtitle

### 2021-08-27 Bernoulli/AnswerReviews.tex

We would like to thank the associate editor and the referees for the attention they paid to our work and for their positive feedbacks.

\bigskip

Minor errors and typos listed by R2 were corrected as suggested. Please find below a few detailed answers.

\begin{itemize}
\item It might have made the paper less scary and dry to read to first provide standard setups (along the lines of what is at the top of p.2), then proceed to the objective (formula (1.2)) and only then supplement all the measure-theoretic setup, e.g. as part of section 2. This would also have yielded the advantage of collecting mathematical notation at the start of section 2 (Is a collection of common notation in tabular form allowed in Bernoulli? This would be a friendly service to the reader.) rather than scattering it over the start of section 1 and section 2.\\
{\em We thank the referee for this suggestion. We postponed the introduction of (1.2)  and the objective of the paper (additive smoothing) after the standard setups (Feynman-Kac path models and hidden Markov models) for better clarity.}
\item p.7 (2.10) and elsewhere uses rectangular brackets as in $\phi_m[\ell_m(\cdot,x_{m+1})]$ which I think is meant to denote $\int_{X_m}\ell_m(x_m,x_{m+1})\phi_m(dx_m)$. This notation has not been introduced. The "Preliminaries" at the top of p.4 have $\mu h$ for the integral of a function $h$ against a measure $\mu$ which would suggest $\phi_m \ell(\cdot,x_{m+1})$. Since the rectangular brackets are used in this sense at many points in the paper, perhaps this notation should be added to the preliminaries.\\
{\em }
\item p.7 Just before 2.2.2, it would be nice to comment on where one might get suitable adjustment weights $\vartheta_n$ from. How are these to be chosen or tuned?\\
{\em We added the following lines after the introduction of the adjustment-weight function (after (2.8): "Adjustment multiplier weights were introduced in [31] to propose data-driven proposal distributions and design robust filtering estimates. These weights usually depend on the new observation and are often chosen to approximate the predictive likelihood of the new observation given the current particle. For further discussions see for instance [7,Chapter~8]".}
\item p. 15-16: for the presentation of Example 2, I feel it would be better to describe the problem fully before giving Durham and Gallant's solution.\\
{\em In Example~2, we thought it would be better to first fully describe the transition density estimator of the process defined by (3.8) before discussing several applications depending on the chosen model for the observation process.}
\item p.29 Appendix A in the supplement has $\phi_n(dx_n)[\ell(\cdot,x_{n+1})]$  in the numerator that arises from $B_n(x_{n+1},dx_n)$. I think this should read $\phi_n(dx_n)\ell(x_n,x_{n+1})$  instead?\\
{\em The normalizing term given in the appendix is correct, see (2.10).}
\item p.30 Appendix A has $\phi_{0:n}L_{0,n}1_{X^n}$  in the denominator for  $\phi_{0:n+1}h$ which I think should read  $\phi_{0:n}L_{0,n}1_{X^{n+1}}$ as there is a dangling $dx_{n+1}$ otherwise.\\
{\em There was indeed a mistake in this identity, thank you for pointing this out. This was corrected using (2.3).}
\end{itemize}

### 2021-08-27 Bernoulli/glo-2020-numerics.tex
Answer Durham-Gallant

In the following we will consider an instance of Example~\ref{eq:durham:gallant}, Case~1, where the latent diffusion $(X_t)_{t > 0}$ is an \emph{Ornstein--Uhlenbeck process} \cite{uhlenbeck1930theory} on $\rset$ parameterised by
$$
\mu(x) = - (x - \theta), \quad \sigma(x) \equiv 1,
$$
where $\theta \in \mathbb{R}$ is a parameter.
This process is assumed to be initialised according to the standard normal distribution. Furthermore, conditionally on $(X_t)_{t > 0}$, observations $(Y_n)_{n \in \nset}$ are generated as
$$
Y_n = (1 - \precpar) \varphi(X_n) + \eta_n, \quad n \in \nsetpos,
$$
where $t_n = \delta n$ for some given observation interval $\delta > 0$, $X_n = X_{t_n}$, $(\eta_n)_{n \in \nsetpos}$ are mutually independent and standard normally distributed noise variables, $\precpar \in \precparsp \eqdef [0, 1]$ is a parameter, and $\varphi$ is a bounded measurable function on $\rset$. We let $\hk_\delta$ denote the (Gaussian) Markov transition kernel of the time-discrete chain $(X_n)_{n \in \nset}$.

@@

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{%OL-version/figures/
        vary_epsilon_fixed_n.png}
        \caption{}
        \label{fig:varying:precpar}
    \end{subfigure}
    ~ 
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{%OL-version/figures/
        fixed_epsilon_vary_n.png}
        \caption{}
        \label{fig:varying:n}
    \end{subfigure}
    \caption{(a) The red line is the deviation of $\postmod{0:n} h_n$ from $\post{0:n} h_n$ for varying $\precpar \in \{0, 0.05, 0.1, \ldots, 0.5 \}$ and fixed $n = 50$, computed by means of Kalman smoothing. Turquoise markers are similar errors obtained on the basis of $60$ replicates of the ideal PaRIS in Algorithm~\ref{alg:ideal:PaRIS} with $\N = 200$ particles and $\K = 2$ backward samples. (b) The red line is the same deviation for increasing $n \in \intvect{1}{50}$ and fixed $\precpar = 0.1$. Then green and blue lines correspond to errors of $60$ independent ideal PaRIS replicates obtained under the skew and true models, respectively, for $\N = 200$ and $\K = 2$.} \label{fig}
\end{figure}

>>>>

In the following we will consider an instance of Example~\ref{eq:durham:gallant}, Case~1, where the latent diffusion $(X_t)_{t > 0}$ is an \emph{Ornstein--Uhlenbeck process} \cite{uhlenbeck1930theory} on $\rset$ parameterised by $\mu(x) = - (x - \theta)$, $\sigma(x) \equiv 1$,  where $\theta \in \mathbb{R}$ is a parameter.
This process is assumed to be initialised according to the standard normal distribution. Furthermore, conditionally on $(X_t)_{t > 0}$, observations $(Y_n)_{n \in \nset}$ are generated as
$$
Y_n = (1 - \precpar) \varphi(X_n) + \eta_n, \quad n \in \nsetpos,
$$
where $t_n = \delta n$ for some given observation interval $\delta > 0$, $X_n = X_{t_n}$, $(\eta_n)_{n \in \nsetpos}$ are mutually independent and standard normally distributed noise variables, $\precpar \in \precparsp \eqdef [0, 1]$ is a parameter, and $\varphi$ is a bounded measurable function on $\rset$. We let $\hk_\delta$ denote the (Gaussian) Markov transition kernel of the time-discrete chain $(X_n)_{n \in \nset}$.

@@

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{%OL-version/figures/
        vary_epsilon_fixed_n.png}
        \caption{}
        \label{fig:varying:precpar}
    \end{subfigure}
    ~ 
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{%OL-version/figures/
        fixed_epsilon_vary_n.png}
        \caption{}
        \label{fig:varying:n}
    \end{subfigure}
    \caption{(a) The red line is the deviation of $\postmod{0:n} h_n$ from $\post{0:n} h_n$ for varying $\precpar \in \{0, 0.05, 0.1, \ldots, 0.5 \}$ and fixed $n = 50$, computed by means of Kalman smoothing. Turquoise markers are similar errors obtained on the basis of $60$ replicates of the ideal PaRIS in Algorithm~\ref{alg:ideal:PaRIS} with $\N = 200$ particles and $\K = 2$ backward samples. (b) The red line is the same deviation for increasing $n \in \intvect{1}{50}$ and fixed $\precpar = 0.1$. Green and blue lines correspond to errors of $60$ independent ideal PaRIS replicates obtained under the skew and true models, respectively, for $\N = 200$ and $\K = 2$.} \label{fig}
\end{figure}
